---
title: "R Notebook"
output: html_notebook
---

# Exercise 0

0. Load data set avocado_df.csv and run the code below to format the dataset. 
```{r}
library(readr)
avocado_df<-read_csv('avocado_df.csv')
```
```{r}
avocado_df$AveragePrice <- as.numeric(avocado_df$AveragePrice)
avocado_df$TotalVolume <- as.numeric(avocado_df$TotalVolume) 
avocado_df$Month <- as.factor(avocado_df$Month) 
avocado_df$Type <- as.factor(avocado_df$Type) 
avocado_df$Region <- as.factor(avocado_df$Region) 
avocado_df$Year <- as.factor(avocado_df$Year) 
```
# Exercise 1


1. Create a linear model of Price as a function of Total Volume and Year.

```{r}
# Solution here


```
2. Print the summary. Interpret the output.

```{r}
# Solution here


```

3a. Get the coefficients of the model and store them as "coefs".

```{r}
# Solution here


```

3b. Run the code below and understand what it is doing.

```{r}
plot(avocado_df$TotalVolume[avocado_df$Year==2015],avocado_df$AveragePrice[avocado_df$Year==2015], xlab= 'Total Volume', ylab = 'Average Price', col = 'black',xlim=c(4,19))
points(avocado_df$TotalVolume[avocado_df$Year==2016],avocado_df$AveragePrice[avocado_df$Year==2016], xlab= 'Total Volume', ylab = 'Average Price', col = 'grey')
points(avocado_df$TotalVolume[avocado_df$Year==2017],avocado_df$AveragePrice[avocado_df$Year==2017], xlab= 'Total Volume', ylab = 'Average Price', col = 'red')
points(avocado_df$TotalVolume[avocado_df$Year==2018],avocado_df$AveragePrice[avocado_df$Year==2018], xlab= 'Total Volume', ylab = 'Average Price', col = 'blue')
legend(x=15,y=3,legend=c('2015','2016','2017','2018'),col=c("black", "grey","red","blue"),pch=1)

abline(coefs[1],coefs[2], col='black')
abline(coefs[1]+coefs[3],coefs[2], col='grey')
abline(coefs[1]+coefs[4],coefs[2], col='red')
abline(coefs[1]+coefs[5],coefs[2], col='blue')
```

4a. Compare this model to the null model using ANOVA.

```{r}
model_constant <- lm(AveragePrice ~ 1 , data=avocado_df)
# Solution here

```

4b. Compare this model to the model with total volume only using ANOVA.

```{r}
model_volume<- lm(AveragePrice ~ 1 + Volume, data=avocado_df)

# Solution here

```
5. Predicted the price of the samples in "unknown_df".

```{r}
unknown_df <- data.frame(TotalVolume=c(15.0,5.0), Type = c("conventional","organic"), Year=c("2016","2015"))

```

# Exercise 2


1. Create a linear model of Price as a function of Total Volume, Year, Type and Total Volume and Type interaction.

```{r}
# Solution here


```

2. Print the summary. Interpret the output.

```{r}
# Solution here


```

3. Get the coefficients of the model and store them as "coefs".

```{r}
# Solution here


```

4a. Compare this model to the null model using ANOVA.

```{r}
model_constant <- lm(AveragePrice ~ 1 , data=avocado_df)
# Solution here

```

4b. Compare this model to the model with total volume only using ANOVA.

```{r}
model_volume<- lm(AveragePrice ~ 1 + TotalVolume, data=avocado_df)
# Solution here

```

4c. Compare this model to the model with Total Volume and Type using ANOVA.

```{r}
model_volume_type <- lm(AveragePrice ~ 1 + TotalVolume + Type, data=avocado_df)
# Solution here

```

4d. Compare this model to the model with Total Volume and Type interaction using ANOVA.

```{r}
model_volume_type_interaction <- lm(AveragePrice ~ 1 + TotalVolume*Type, data=avocado_df)
# Solution here

```

4e. Compare this model to the model with Total Volume and Year using ANOVA.

```{r}
model_year <- lm(AveragePrice ~ 1 + Year, data=avocado_df)
# Solution here


```
5. Predicted the price of the samples in "unknown_df".

```{r}
# Solution here
unknown_df <- data.frame(TotalVolume=c(15.0,5.0), Type = c("conventional","organic"), Year=c("2016","2015"))

```

