---
title: "R Notebook"
output: html_notebook
---


# Exercise 0

0. Load data set avocado_df_categories.csv and run the code below to format the dataset. 
```{r}
library("readr")
avocado_df<-read_csv('avocado_df_categories.csv')
avocado_df$PriceCategory <- factor(avocado_df$PriceCategory, levels= c("Cheap","Expensive"),labels=c(0,1))
avocado_df$TotalVolume <- as.numeric(avocado_df$TotalVolume) 
avocado_df$Type <- as.factor(avocado_df$Type) 
avocado_df$Month <- as.factor(avocado_df$Month) 
avocado_df$Year <- as.factor(avocado_df$Year) 
```
# Exercise 1: Model with Price and Type Interaction

1. Run the code below to create a logistic model with price and type interaction variable.

```{r}
#solution here

model_volume_type_interaction <- glm(PriceCategory ~ 1 + TotalVolume*Type, data=avocado_df, family='binomial')
```

2. Print the summary of the model.

```{r}
#solution here

summary(model_volume_type_interaction)
```
3. Interpret the output of summary. What do the coefficients mean?

1. Model for conventional avocado -- log(P/(1-P)) = 2.24 - 0.28 * TotalVolume

When total demand is zero, the log odds is 2.24. If total volume increases by 1, the log odds decrease by -0.28.

2. Model for organic avocado -- log(P/(1-P))= 3.53 - 0.23 * TotalVolume

When total demand is zero, the log odds is 2.24. If total volume increases by 1, the log odds decrease by -0.28.


4. What are the predicted probabilities for the dataset, df, below?

```{r}
df = data.frame(TotalVolume=c(15.0,5.0), Type=c("conventional","organic"))
```

```{r}
#solution here

log_odds <-predict(model_volume_type_interaction,df)
probs <- exp(log_odds)/(1+exp(log_odds))
print(probs)
```

5. With a threshold value of 0.5, print the confusion matrix of the logistic model.

```{r}
library(caret)

#solution here

probabilities <- model_volume_type_interaction$fitted.values
predicted_classes = as.numeric(probabilities > 0.5)
print(predicted_classes)
confusionMatrix(data=factor(predicted_classes),reference=avocado_df$PriceCategory, positive="1")
```

6. Compare the model with the null model. Is there a siginificant decrease in the deviance?

```{r}
#solution here

model_constant <- glm(PriceCategory ~ 1, data=avocado_df, family='binomial')
anova(model_constant, model_volume_type_interaction, test='Chisq')
```

7. Compare the model aganist the model with no interaction term between price and type. Is there a siginificant decrease in the deviance?

```{r}
#solution here

model_volume_type <- glm(PriceCategory ~ 1 + TotalVolume + Type, data=avocado_df, family='binomial')
anova(model_volume_type, model_volume_type_interaction, test='Chisq')
```

# Exercise 2: Model with Price, Type and Year.

1. Create a model with price and type interaction variable.

```{r}
#solution here

model_volume_type_year <- glm(PriceCategory ~ 1 + Year + Type + TotalVolume, data=avocado_df, family='binomial')
```

2. Print the summary of the model.

```{r}
#solution here

summary(model_volume_type_year)
```
3. Interpret the output of summary. What do the coefficients mean?

i) If the sample is conventional and taken in 2015,

log P/(1-P) =  1.91 -0.29*(Total Volume)

When total demand is zero, the log odds is 1.91. If total volume increases by 1, the log odds decrease by -0.29.

ii) If the sample is conventional and taken in 2016,

log P/(1-P) = 1.84 - 0.29*(Total Volume)

When total demand is zero, the log odds is 1.84. If total volume increases by 1, the log odds decrease by -0.29.

iii) If the sample is conventional and taken in 2017,

log P/(1-P) =  2.11 - 0.29*(Total Volume)

When total demand is zero, the log odds is 1.91. If total volume increases by 1, the log odds decrease by -0.29.

iv) If the sample is conventional and taken in 2018,

log P/(1-P) = 2.17 - 0.29*(Total Volume)

When total demand is zero, the log odds is 2.17. If total volume increases by 1, the log odds decrease by -0.29.

v) If the sample is organic and taken in 2015,

log P/(1-P) = 3.85-0.29*(Total Volume)

When total demand is zero, the log odds is 3.85. If total volume increases by 1, the log odds decrease by -0.29.

vi) If the sample is organic and taken in 2016,

log P/(1-P) =  3.78 - 0.29*(Total Volume)

When total demand is zero, the log odds is 3.78. If total volume increases by 1, the log odds decrease by -0.29.

vii) If the sample is organic and taken in 2017,

log P/(1-P) =  5.05 - 0.29*(Total Volume)

When total demand is zero, the log odds is 5.05. If total volume increases by 1, the log odds decrease by -0.29.

viii) If the sample is organic and taken in 2018,

log P/(1-P) =  5.11 - 0.29*(Total Volume)

When total demand is zero, the log odds is 5.11. If total volume increases by 1, the log odds decrease by -0.29.

4. What are the predicted probabilities for the dataset, df, below?

```{r}
#solution here

df = data.frame(TotalVolume=c(12.0,10.0), Type=c("conventional","organic"), Year=c(2017,2015))
log_odds <-predict(model_volume_type_interaction,df)
probs <- exp(log_odds)/(1+exp(log_odds))
print(probs)
```

5. With a threshold value of 0.5, print the confusion matrix of the logistic model.

```{r}
library(caret)

#solution here

probabilities <- model_volume_type_year$fitted.values
predicted_classes = as.numeric(probabilities > 0.5)
print(predicted_classes)
confusionMatrix(data=factor(predicted_classes),reference=avocado_df$PriceCategory, positive="1")
```

6. Compare the model with the null model. Is there a siginificant decrease in the deviance?

```{r}
#solution here

model_constant <- glm(PriceCategory ~ 1, data=avocado_df, family='binomial')
anova(model_constant, model_volume_type_year, test='Chisq')
```

7. Compare the model aganist the model with no interaction term between price and type. Is there a siginificant decrease in the deviance?

```{r}
#solution here

model_volume_type <- glm(PriceCategory ~ 1 + TotalVolume + Type, data=avocado_df, family='binomial')
anova(model_volume_type, model_volume_type_year, test='Chisq')
```