---
title: "Logistic Regression Code"
output: html_document
---

# Load and Format data
Here, we read and format data.
```{r}
library("readr")
avocado_df<-read_csv('avocado_df_categories.csv')
avocado_df$PriceCategory <- factor(avocado_df$PriceCategory, levels= c("Cheap","Expensive"),labels=c(0,1))
avocado_df$TotalVolume <- as.numeric(avocado_df$TotalVolume) 
avocado_df$Type <- as.factor(avocado_df$Type) 
avocado_df$Region <- as.factor(avocado_df$Region) 
avocado_df$Month <- as.factor(avocado_df$Month) 
avocado_df$Year <- as.factor(avocado_df$Year) 
```

# Summary of Data

```{r}
head(avocado_df)
```

```{r}
summary(avocado_df)
```

# Logistic Regression in R

## Total Volume + Constant Term

We will now build a logistic model with a constant term and a TotalVolume term.

```{r}
# create model with PriceCategory vs AveragePrice, family='binomial'

```
### Model Summary

```{r}
# Print model summary

```

You can also get the coefficents of the model.

```{r}
# print model ceofs

```


### Predicting Class Probabilities
```{r}

unknown_df <- data.frame(TotalVolume=15.0)
# store prediction of unknown_df as log_odds
```

```{r}
# get convert log odds to probability


```

### Getting Class Probabilities of Data

We can get the probability estimates of the model.
```{r}
# get fitted.values and store in probabilities

# print head of probabilities
```

```{r}
# print PriceCategory from avocado_df

```



### Predicting Class from Class Probabilities

Using a threshold value and the probabilities, we can assign classes to each observation.

### Predicting Classes

```{r}
# create boolean probabilities > 0.5
# coerce to numeric and store as predicted_classes

# print predicted_classes

```
Let's see our actual classes.
```{r}
# print the actual classes

```

### Confusion Matrix

We can calculate the error in our prediction.
```{r}
library(caret)
# confusionMatrix with data=factor(predicted_classes) and reference=avocado_df$PriceCategory



```

## Model with Constant Term

We will now build a logistic model with a constant term.

```{r}
# model with a constant term, family='binomial'


```
### Model Summary

```{r}
# print summary

```
## Model Comparison

We can compare models using the anova function.

```{r}
# compare model volume to model constant,  test='Chisq'


```



## Model with Volume and Type 

### Create Model
```{r}
# create model with TotalVolume and Type, family='binomial'


```

### Model Summary

```{r}
summary(model_volume_type)
```

### Predicting Class Probabilities
```{r}
unknown_df <-  data.frame(TotalVolume=c(15.0,5.0), Type=c("conventional","organic"))
# store prediction of unknown_df as log_odds


```

```{r}
# get convert log odds to probability


```

### Getting Class Probabilities of Data

We can get the probability estimates of the model.
```{r}
# get fitted.values and store in probabilities

# print head of probabilities


```

```{r}
# print PriceCategory from avocado_df

```



### Predicting Class from Class Probabilities

Using a threshold value and the probabilities, we can assign classes to each observation.

### Predicting Classes

```{r}
# create boolean probabilities > 0.5
# coerce to numeric and store as predicted_classes

# print predicted_classes

```
Let's see our actual classes.
```{r}
# print the actual classes

```

### Confusion Matrix

We can calculate the error in our prediction.
```{r}
# confusionMatrix with data=factor(predicted_classes) and reference=avocado_df$PriceCategory



```
## Model Comparison

We can compare models using the anova function.

```{r}
# compare model_constant to model_volume_type,  test='Chisq'


```

```{r}
# compare model_volume to model_volume_type,  test='Chisq'


```


