---
title: "linear_model_exercises"
output: html_document
---
# Exercise 0:

Load the library below.

```{r}
library(pscl)
```
## Exercise 1: Model with fem, ment_cat.

As seen from the box plots in the presentation and below, the mean of the distributions for each ment might not be linear. 

```{r}
library(reshape2)
```

```{r}
df.men <- melt(bioChemists[bioChemists$fem == "Men",c("ment","art")], id.var = "ment")

ggplot(data = df.men, aes(x=ment, y=value)) +  geom_boxplot(aes(group=ment))
```

```{r}
df.women <- melt(bioChemists[bioChemists$fem == "Women",c("ment","art")], id.var = "ment")
ggplot(data = df.women, aes(x=ment, y=value)) +  geom_boxplot(aes(group=ment)) + ggtitle("Box plot of art vs ment for women")
```

0. It might be better to treat each ment numerical value as a category. Run the code below to create a new column with ment categories.

```{r}
#solution here

bioChemists$ment_cat <- as.factor(bioChemists$ment)
```

1. Create a model with fem and ment_cat.

```{r}
#solution here

model_sex_ment_cat <-glm(art ~ 1 + fem + ment_cat, data = bioChemists,family = poisson(link = log))
```

2. Print the summary of the model.

```{r}
#solution here

summary(model_sex_ment_cat)
```

3. Using ANOVA, compare this model to the model with only fem.

```{r}
#solution here

model_sex <-glm(art ~ 1 + fem, data = bioChemists,family = poisson(link = log))
anova(model_sex, model_sex_ment_cat, test='Chisq')
```

4. Is the model with ment_cat better than the model with ment?

Not necessarily. While the model with sex and ment_cat has a lower deviance than the model sex and ment, the former uses much more degrees of freedom than the latter.

## Exercise 2: Model with fem, ment interaction

1. Run the code below to create a model with  fem and ment interaction.

```{r}
#solution here

model_sex_ment_interaction <- glm(art ~ 1 + fem*ment, data=bioChemists, family=poisson(link=log))
```

2. Print the summary of the model.

```{r}
#solution here

summary(model_sex_ment_interaction)
```

3. Interpret the model.

i) For men,
  log(lambda) = 0.351 + 0.024*ment
- log(lambda) = 0.351 when ment = 0
- A 1 unit increase in ment causes 0.024 increase in lambda.

ii) For women,
  log(lambda) = 0.16 + 0.025*ment
- log(lambda) = 0.16 when ment = 0
- A 1 unit increase in ment causes 0.025 increase in lambda.


4. Interpret the significance of effect of the interaction coefficient. 

The interaction coefficient is statistically equivalent 0.

5. Compare the model with ment and sex interaction to the model with no interaction between ment and sex. 
```{r}
#solution here

anova(model_sex_ment, model_sex_ment_interaction, test='Chisq')
```

## Exercise 3: Model with fem, ment, phd

1. Run the code below to create a model with  fem, ment and phd.

```{r}
#solution here

model_sex_ment_phd <- glm(art ~ 1 + fem + ment + phd, data=bioChemists, family=poisson(link=log))
```

2. Print the summary of the model.

```{r}
#solution here

summary(model_sex_ment_phd)
```

3. Interpret the model.

i) For men,
  log(lambda) = 0.351 + 0.024*ment + 0.011*phd
- log(lambda) = 0.351 when ment = 0
- A 1 unit increase in ment causes 0.024 increase in lambda, holding phd constant.
- A 1 unit increase in ment causes 0.011 increase in lambda, holding ment constant.

ii) For women,
  log(lambda) = 0.16 + 0.025*ment + 0.011*phd
- log(lambda) = 0.16 when ment = 0
- A 1 unit increase in ment causes 0.025 increase in lambda, holding phd constant.
- A 1 unit increase in ment causes 0.011 increase in lambda, holding ment constant.


4. Interpret the significance of effect of the phd coefficient. 

The phd coefficient is statistically equivalent 0.

5. Compare the model with ment, sex and phd to the model with ment and sex only. 
```{r}
#solution here

anova(model_sex_ment, model_sex_ment_phd, test='Chisq')
```
