---
title: "linear_model_exercises"
output: html_document
---
# Exercise 0:

Load the library below.

```{r}
library(pscl)
```
## Exercise 1: Model with fem, ment_cat.

As seen from the box plots in the presentation and below, the mean of the distributions for each ment might not be linear. 

```{r}
library(reshape2)
```

```{r}
df.men <- melt(bioChemists[bioChemists$fem == "Men",c("ment","art")], id.var = "ment")

ggplot(data = df.men, aes(x=ment, y=value)) +  geom_boxplot(aes(group=ment))
```

```{r}
df.women <- melt(bioChemists[bioChemists$fem == "Women",c("ment","art")], id.var = "ment")
ggplot(data = df.women, aes(x=ment, y=value)) +  geom_boxplot(aes(group=ment)) + ggtitle("Box plot of art vs ment for women")
```

0. It might be better to treat each ment numerical value as a category. Run the code below to create a new column with ment categories.

```{r}
bioChemists$ment_cat <- as.factor(bioChemists$ment)
```

1. Create a model with fem and ment_cat.

```{r}
#solution here

```

2. Print the summary of the model.

```{r}
#solution here

```

3. Using ANOVA, compare this model to the model with only fem.

```{r}
#solution here


```

4. Is the model with ment_cat better than the model with ment?


## Exercise 2: Model with fem, ment interaction

1. Run the code below to create a model with  fem and ment interaction.

```{r}
#solution here

```

2. Print the summary of the model.

```{r}
#solution here

```

3. Interpret the model.

i) For men

ii) For women

4. Interpret the significance of effect of the interaction coefficient. 


5. Compare the model with ment and sex interaction to the model with no interaction between ment and sex. 
```{r}
#solution here

```

## Exercise 3: Model with fem, ment, phd

1. Run the code below to create a model with  fem, ment and phd.

```{r}
#solution here

```

2. Print the summary of the model.

```{r}
#solution here

```

3. Interpret the model for each of the cases below

i) For men

ii) For women



4. Interpret the significance of effect of the phd coefficient. 


5. Compare the model with ment, sex and phd to the model with ment and sex only. 

```{r}
#solution here

```
