---
title: "Poisson Regression Code"
output: html_document
---

# Load and Format data
Here, we read and format data.
```{r}
library("pscl")
bioChemists$kid5 <- factor(bioChemists$kid5)
```

# Summary of Data

```{r}
head(bioChemists)
```

```{r}
summary(bioChemists)
```

# Poisson Regression in R

## Constant Term

We will now build a logistic model with a constant term and a TotalVolume term.

```{r}
model_constant <-glm(art ~ 1, data = bioChemists,family = poisson(link = log))
```
### Model Summary

```{r}
summary(model_constant)
```

You can also get the coefficents of the model.

```{r}
print(coef(model_constant))
```

## Model with Constant + Gender Term

We will now build a Poisson model with a constant term and sex.

```{r}
model_sex <-glm(art ~ 1 + fem, data = bioChemists,family = poisson(link = log))
```
### Model Summary

```{r}
summary(model_sex)
```
## Model Comparison

We can compare models using the anova function.

```{r}
anova(model_constant, model_sex, test='Chisq')
```



## Model with fem and ment 

### Create Model
```{r}
model_sex_ment <- glm(art ~ 1 + fem + ment, data=bioChemists, family=poisson(link=log))
```

### Model Summary

```{r}
summary(model_sex_ment)
```


### Anova with null model

```{r}
anova(model_constant, model_sex_ment, test='Chisq')
```

### Anova with model with only sex

```{r}
anova(model_sex, model_sex_ment, test='Chisq')
```



