---
title: "Poisson Regression Code"
output: html_document
---

# Load and Format data
Here, we read and format data.
```{r}
library("pscl")
bioChemists$kid5 <- factor(bioChemists$kid5)
```

# Summary of Data

```{r}
# print head of dataset

```

```{r}
# print summary of dataset

```

# Poisson Regression in R

## Constant Term

We will now build a logistic model with a constant term and a TotalVolume term.

```{r}
# model with constant term,  poisson(link = log))


```
### Model Summary

```{r}
# print model summary

```

You can also get the coefficents of the model.

```{r}
# print model coefs


```


## Model with Constant + Gender Term

We will now build a Poisson model with a constant term and sex.

```{r}
# poisson glm with fem and constant, family = poisson(link = log)) as model_sex


```
### Model Summary

```{r}
# print model summary

```



## Model Comparison

We can compare models using the anova function.

```{r}
# compare model_constant vs. model_sex


```



## Model with fem and ment 

### Create Model
```{r}
# poisson glm with fem, constant, ment family = poisson(link = log)) as model_sex_ment


```

### Model Summary

```{r}
# print model summary

```


### Anova with null model

```{r}

# compare model_constant and model_sex_ment

```

### Anova with model with only sex

```{r}
# compare model_sex and model_sex_ment

```



